Thesis outline

### 2017-06-15 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Edits to Abstract, Intro, Appendix
Updates to Ch. 5-7

\chapter[Conclusion]{Conclusions and suggestions for future work}

% Papers 1-3
\section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}
We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample, but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances, 
10\% lower nitrogen abundances, and 17\% lower N/O ratios than star-forming 
dwarf galaxies in denser regions.  The large-scale ($\sim 10$ \hMpc) environment 
influences the chemical evolution of star-forming dwarf galaxies.

In addition to studying the large-scale environmental influence on the 
distribution of gas-phase chemical abundances in star-forming dwarf galaxies, we 
also investigate if and how the large-scale environment affects relationships 
between the chemical abundances and various other physical properties of the 
galaxies.  We find that the N/O ratio decreases with increasing metallicity 
rather than a constant value for the N/O ratio as a function of O/H as observed 
in other studies.  This is contrary to what we see in the $M_*$-N/O 
relationship, where we find that some of the star-forming dwarf galaxies have a 
constant value of N/O for a range of masses while the remainder exhibit a 
positive relationship between the stellar mass and N/O ratio.  We make note of a 
different critical mass in the $M_*$-N/O relationship in the two environments, 
where the void dwarf galaxies begin to show evidence of secondary nitrogen 
synthesis at a stellar mass $\sim$0.4 dex lower than for the galaxies in denser 
regions.  Most of our star-forming dwarf galaxies follow the established 
mass-metallicity relation \citep[e.g.,][]{Tremonti04}.

No relationship is observed between the metallicity and \ion{H}{1} mass in our 
sample of star-forming dwarf galaxies, but we find that the N/O ratio decreases 
with increasing \ion{H}{1} mass for a given stellar mass.  The star-forming 
dwarf galaxies also exhibit an increase in the metallicity and N/O ratio with 
increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
SFR for either metallicity or the N/O ratio in dwarf galaxies, but the 
metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
environmental influence on the distributions of the gas-phase chemical 
abundances and the critical mass in the $M_*$-N/O relationship, we do not 
observe any significant differences between the star-forming void and wall dwarf 
galaxies in any of these relationships.

We surmise that the differences in the distributions of metallicity and the N/O 
ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
environmental influence on their star formation history and evolution.  The 
shift in the gas-phase oxygen abundance distribution could be observational 
evidence for delayed star formation in void galaxies when compared to those in 
denser regions.  This would result in a smaller ratio of stellar mass to dark 
matter halo mass in void galaxies than in dwarf galaxies in denser regions, as 
predicted in simulations by \cite{Jung14} and \cite{Tonnesen15}.  If the void 
galaxies are retaining more oxygen as a result of their deeper potential wells, 
then they would be able to commence secondary nitrogen synthesis earlier, as 
seen in the $M_*$-N/O relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
that cosmological downsizing is environmentally dependent as predicted by 
\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
in void dwarf galaxies whose dark matter halos ceased coalescing earlier than 
for dwarf galaxies in denser regions.

@@

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
oxygen and nitrogen abundances than average.  This matches the results of 
\cite{Park09}, who find that late-late type galaxy pairs within 0.05$r_{vir}$ 
are bluer and have higher SFRs.  In contrast, dwarf galaxies within 0.1 \hMpc of 
the center of the closest group are redder, have lower oxygen abundances, and 
have higher N/O ratios than average.  These results are independent of both the 
maximum relative velocity required to define a nearest neighbor and the sample 
(star-forming versus all dwarf galaxies).

When we incorporate the redshift into the distance calculations, we find that 
the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
merging with their nearest neighbor.  These merging galaxies likely share the 
same dark matter halo, suggesting that the dark matter halo is more influential 
on a galaxy's evolution than the distance between a galaxy and its nearest 
neighbor.

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD) in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a value less than 25 for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

@@

There is a higher fraction of faint galaxies from denser regions than faint void 
galaxies in the green valley.  Combined with the previous results about the 
large-scale environmental influence on the gas-phase chemical abundances, this 
indicates that void dwarf galaxies are less evolved than dwarf galaxies in 
denser environments.

@@

>>>>

\chapter[Conclusion]{Conclusions and suggestions for future work}\label{ch:conclusion}

% Papers 1-3
\section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}

We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

% Shift in O/H
By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample, but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances 
than star-forming dwarf galaxies in denser regions.  This shift in the gas-phase 
oxygen abundance distribution could be observational evidence for delayed star 
formation in void galaxies when compared to those in denser regions.  This would 
result in a smaller ratio of stellar mass to dark matter halo mass in void 
galaxies than in dwarf galaxies in denser regions, as predicted in simulations 
by \cite{Jung14} and \cite{Tonnesen15}.  If the void galaxies are retaining more 
oxygen as a result of their deeper potential wells (relative to galaxies of the 
same stellar mass in dense regions), then they would be able to commence 
secondary nitrogen synthesis earlier.  We find that some of the star-forming 
dwarf galaxies have a constant value of N/O for a range of masses while the 
remainder exhibit a positive relationship between the stellar mass and N/O ratio 
in the $M_*$-N/O relationship.  We make note of a different critical mass in the 
$M_*$-N/O relationship in the two environments, where the void dwarf galaxies 
begin to show evidence of secondary nitrogen synthesis at a stellar mass 
$\sim$0.4 dex lower than for the galaxies in denser regions.  This indicates 
that the void galaxies synthesize secondary nitrogen at a smaller stellar mass 
than galaxies in denser regions.

% Shift in N/O
We also find that star-forming void dwarf galaxies have 17\% lower N/O ratios 
than star-forming dwarf galaxies in denser regions.  This shift towards lower 
N/O ratios in the star-forming dwarf galaxies might be evidence that 
cosmological downsizing is environmentally dependent as predicted by 
\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
and cool gas available to fuel star formation up to the present epoch in void 
dwarf galaxies whose dark matter halos ceased coalescing earlier than for dwarf 
galaxies in denser regions.  We surmise that the differences in the 
distributions of metallicity and the N/O ratio seen in the sample of 
star-forming dwarf galaxies are due to a large-scale ($\sim$10 \hMpc) 
environmental influence on their star formation history and evolution.

% HI mass
In addition to studying the large-scale environmental influence on the 
distribution of gas-phase chemical abundances in star-forming dwarf galaxies, we 
also investigate if and how the large-scale environment affects relationships 
between the chemical abundances and various other physical properties of the 
galaxies.  Most of our star-forming dwarf galaxies follow the established 
mass-metallicity relation \citep[e.g.,][]{Tremonti04}.  No relationship is 
observed between the metallicity and \ion{H}{1} mass in our sample of 
star-forming dwarf galaxies, but we find that the N/O ratio decreases with 
increasing \ion{H}{1} mass for a given stellar mass.  Because most of our dwarf 
galaxies are in the low metallicity tail of the mass-metallicity relation and 
there is a strong correlation between stellar mass and \ion{H}{1} mass, it is 
not surprising that we see no relationship between the metallicity and 
\ion{H}{1} mass.  The inverse relationship between the N/O ratio and the 
\ion{H}{1} mass is due to the time delay in the production of nitrogen relative 
to oxygen.

% Color
The star-forming dwarf galaxies exhibit an increase in the metallicity and N/O 
ratio with increasing color (both $u-r$ and $g-r$).  Older, redder galaxies have 
had more time to convert their hydrogen into heavier elements through star 
formation, thus increasing their metallicities.  The correlation between the N/O 
ratio and the color of a galaxy indicates a time delay between the release of 
oxygen and nitrogen.

% (s)SFR
We see very little correlation with SFR for either metallicity or the N/O ratio 
in dwarf galaxies, but the metallicity and N/O ratio decrease with increasing 
sSFR.  While we expect a relationship between the SFR and the metallicity due to 
the fundamental relationship, our range of metallicity values might not extend 
high enough to detect a significant relationship with the SFR in our sample of 
star-forming dwarf galaxies.  The strong anti-correlation with low dispersion 
between the N/O ratio and the sSFR in our dwarf galaxies might be evidence that 
oxygen in produced in higher mass stars than those which synthesize nitrogen.

%Beyond the large-scale 
%environmental influence on the distributions of the gas-phase chemical 
%abundances and the critical mass in the $M_*$-N/O relationship, we do not 
%observe any significant differences between the star-forming void and wall dwarf 
%galaxies in any of these relationships.

@@

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.1$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.1$r_{vir}$ tend to be bluer, have a higher sSFR, and have higher 
oxygen and nitrogen abundances than average.  This matches the results of 
\cite{Park09}, who find that higher luminosity late-late type galaxy pairs 
within 0.05$r_{vir}$ are bluer and have higher SFRs.  In contrast, dwarf 
galaxies within 0.1 \hMpc of the center of the closest group are redder, have 
lower oxygen abundances, and have higher N/O ratios than average.  These results 
are independent of both the maximum relative velocity required to define a 
nearest neighbor and the sample (star-forming versus all dwarf galaxies).

When we incorporate the redshift into the distance calculations, we find that 
the galaxies within 0.1$r_{vir}$ are most likely strongly interacting or merging 
with their nearest neighbor.  These merging galaxies likely share the same dark 
matter halo, suggesting that the dark matter halo is more influential on a 
galaxy's evolution than the distance between a galaxy and its nearest neighbor.

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD) in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a value aimc$< 25$ for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

@@

The fraction of void galaxies that are found in the green valley is 
significantly smaller than the fraction of green valley galaxies found in denser 
regions.  Combined with the previous results about the large-scale environmental 
influence on the gas-phase chemical abundances, this indicates that void dwarf 
galaxies are less evolved than dwarf galaxies in denser environments.

@@

We find that the N/O ratio decreases with increasing metallicity rather than a 
constant value for the N/O ratio as a function of O/H as observed in other 
studies.  This variation of the behavior of the N/O ratio is contrary to what we 
see in the $M_*$-N/O relationship, where our dwarf galaxies exhibit either a 
constant value (nitrogen plateau) or an increase in (secondary nitrogen 
production) the N/O ratio for increasing stellar mass.  It appears as though the 
extremely low-metallicity galaxies present in the metallicity-N/O relationship 
are causing this unusual behavior.  Detailed observations and high-resolution 
spectra are needed of this population of galaxies, to confirm their metallicity 
estimates and gain insight into this unique relationship.
